NFL Draft Analysis

### 2020-05-12 draft_analysis.Rmd
Add lm line to all the graphs (in addition to the loess lines)

qb_av_pick <- master_df %>%
  filter(year >= 2000) %>%
  filter(Pos == "QB") %>%
  ggplot(mapping=aes(x=Pick, y=CarAV)) +
    geom_point()  +
    labs(x = "Pick", y = "Career Value", title = "Average Value over picks for QBs Drafted in the 2000s") + 
    geom_smooth(method='loess')

@@

qb_av_pick <- master_df %>%
  filter(year >= 2000) %>%
  filter(Pos == "QB") %>%
  ggplot(mapping=aes(x=Pick, y=CarAV)) +
    geom_point()  +
    labs(x = "Pick", y = "Career Value", title = "QB Average Value") + 
    geom_smooth(method='loess')

rb_av_pick <- master_df %>%
  filter(year >= 2000 & Pos == "RB") %>%
  ggplot(mapping=aes(x=Pick, y=CarAV)) +
    geom_point()  +
    labs(x = "Pick", y = "Career Value", title = "RB Average Value") + 
    geom_smooth(method='loess')

wr_av_pick <- master_df %>%
  filter(year >= 2000 & Pos == "WR") %>%
  ggplot(mapping=aes(x=Pick, y=CarAV)) +
    geom_point()  +
    labs(x = "Pick", y = "Career Value", title = "WR Average Value") + 
    geom_smooth(method='loess')

>>>>

qb_av_pick <- master_df %>%
  filter(year >= 2000) %>%
  filter(Pos == "QB") %>%
  ggplot(mapping=aes(x=Pick, y=CarAV)) +
    geom_point()  +
    labs(x = "Pick", y = "Career Value", title = "Average Value over picks for QBs Drafted in the 2000s") + 
    geom_smooth(method='loess') + 
    geom_smooth(method=lm, color="green")

@@

qb_av_pick <- master_df %>%
  filter(year >= 2000) %>%
  filter(Pos == "QB") %>%
  ggplot(mapping=aes(x=Pick, y=CarAV)) +
    geom_point()  +
    labs(x = "Pick", y = "Career Value", title = "QB Average Value") + 
    geom_smooth(method='loess') + 
    geom_smooth(method=lm, color="green")

rb_av_pick <- master_df %>%
  filter(year >= 2000 & Pos == "RB") %>%
  ggplot(mapping=aes(x=Pick, y=CarAV)) +
    geom_point()  +
    labs(x = "Pick", y = "Career Value", title = "RB Average Value") + 
    geom_smooth(method='loess') + 
    geom_smooth(method=lm, color="green")

wr_av_pick <- master_df %>%
  filter(year >= 2000 & Pos == "WR") %>%
  ggplot(mapping=aes(x=Pick, y=CarAV)) +
    geom_point()  +
    labs(x = "Pick", y = "Career Value", title = "WR Average Value") + 
    geom_smooth(method='loess') + 
    geom_smooth(method=lm, color="green")
